Incentivizing Exploration with Unbiased Histories

### 2019-04-16 model.tex
Moved (anti)concentration theorems back to prelims.

Throughout the paper, we use the standard concentration and anti-concentration inequalities: respectively, Chernoff Bounds and Berry-Esseen Theorem. The former states that that a sum of independent random variables converges to its expectation quickly. The latter states that the CDF of an appropriately scaled average of IID random variables converges to the CDF of the standard normal distribution pointwise. In particular, the average strays far enough from its expectation with some guaranteed probability. The theorem statements are moved to Appendix~\ref{sec:prelim}.

>>>>

Throughout the paper, we use the standard concentration and anti-concentration inequalities: respectively, Chernoff Bounds and Berry-Esseen Theorem. The former states that 
    $\bar{X} = \frac{1}{n}\sum_{i=1}^n X_i$, 
the average of $n$ independent random variables $X_1 \LDOTS X_n$, converges to its expectation quickly. The latter states that the CDF of an appropriately scaled average $\bar{X}$ converges to the CDF of the standard normal distribution pointwise. In particular, the average strays far enough from its expectation with some guaranteed probability. The theorem statements are as follows:

\begin{theorem}
Fix $n$. Let $X_1,...,X_n$  be independent random variables, and let $\bar{X} = \frac{1}{n}\sum_{i=1}^n X_i$. Then:

\begin{itemize}
\item[(a)] \emph{(Chernoff Bounds)} %\label{thm:prelims-chernoff}
Assume $X_i \in [0,1]$ for all $i$. Then
\[
\Pr[ |\bar{X} - \E[\bar{X}]| > \varepsilon] \leq 2\exp(-2n\varepsilon^2).
\]

\item[(b)] \emph{(Berry-Esseen Theorem)} %\label{thm:prelims-Berry}
Assume $X_1 \LDOTS X_n$ are identically distributed, with 
\[ 
    \sigma^2 := \E[ (X_1 - \E[X_1])^2] = \sigma^2
    \quad\text{and}\quad
    \rho := \E[ |X_1 - \E[X_1]|^3] <\infty.\]
Let $F_n$ be the cumulative distribution function of $\frac{(\bar{X} - \E[\bar{X}]) \sqrt{n}}{\sigma}$ and $\Phi$ be the cumulative distribution function of the standard normal distribution. 
\[
|F_n(x) - \Phi(x) | \leq \frac{\rho}{2\sigma^3\sqrt{n}}
\quad \forall x\in \R.
\]
\end{itemize}
\end{theorem}
